Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-10 response_to_review_SOLA-D-20-00015_v1.txt

Dear Editor,

Thank you very much for your email with the report on the first version of our manuscript ID SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".

We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read. We found all queries very relevant, with useful and constructive criticisms and suggestions. We believe we addressed all points, as a result of which we believe the manuscript has gained in both content and clarity.

Below, we copy/paste all queries (Q) of the review. Following each query we include an answer (A), commenting the changes in the manuscript, in which all edited/new text is highlighted in red color font.

@@

Looking forward to your response. Sincerely,
The Authors.

------------------------------beginning of review and response---------------------------
COMMENTS FOR THE AUTHOR:

@@

Review of Thermodynamic Structure of the Solar corona: tomographic reconstructions and MHD modeling

This is a well-structured and clearly-written paper, presenting a detailed comparison of tomographic reconstructions of the low solar corona (which gives density and temperature), and a global MHD model. The work is important and valuable to the field, and is suitable for publication in Solar Physics. There are no major scientific concerns. The paper should be ready for publication if the following, mostly minor, concerns are addressed:

Medium concerns
-----------------------------------------------------------------------------------------
Q1. All of the multi-panel figures that show longitude-latitude maps (e.g. figure 1, 2, 3 etc) are too small, it is very difficult to see any details. There is a lot of white space between the panels that can be removed, and this would be one way to instantly make the maps larger.

A1. We agree. We improved the use of space in the long-lat maps in Figures 1, 2, 8 and 9, while the one in Figure 3 remains the same (we believe those are fine).

-----------------------------------------------------------------------------------------
Q2. Figure 3 and 11, bottom panels. I find it difficult to distinguish between the red and magenta colours. Can you replace magenta with a different colour, maybe green?

A2. We agree. Actually this affects all following Figures: 3, 4, 11, and 14. In those, we applied the following changes: Red->Orange and Magenta->Red. These emulate our previous choice of colors in Nuevo et al. (2013) and Lloveras et al. (2017). We like to keep all "up" structures in a "warm" palette. We edited text accordingly all along the manuscript. We believe the colors are now clearly distinguishable in all figures.

-----------------------------------------------------------------------------------------
Q3. Page 14, paragraph starting at line 34. You discuss the latitudinal distribution of short and long loops, and state that the small legs mainly populate the equatorial latitudes, and longer legs at higher latitudes. But this is a skewed result - their spatial positioning was a criteria for their categorisation, so this should not be presented as a scientific result.

A3. Several aspects are involved here, the discussion in the paragraph you indicate heavily depends on that in the final paragraph of Section 2.3. Both were confusing as they were, specially the latter, so we edited both. Actually, we do not say that *small* legs populate the equatorial latitudes and *large* ones the mid latitudes. We say that if one classifies the *small-closed* loops in DOWN and UP, the former peak near the equator and the latter peak near mid latitudes (at least for the deep minimum rotation CR-2082). The classification of legs in four classes in Section 2.3 includes limits for the latitude of their footpoints, to distinguish different layers of the streamer belt (legs of type 0, I and II), as well as to separate field lines of the high latitude CHs (legs of type III). We included two new panels in Figure 3, showing frequency histograms of the latitude of the four types of legs at 1.105 Rsun. Within the range Abs(latitude) < 50 deg, and for the solar minimum target CR-2082, down-legs are peaked near the equator while up-legs peak at mid-latitudes. This is less obvious for CR-2208, although it is clear that down-legs peak in the core of the streamer belt. Now, it turns out that down-legs are scarce for Abs(latitude) > 50 deg. Should have we not included the limit of Abs(latitude) < 50 deg for closed-small down and up legs (i.e., legs of type 0 and I), their histograms would still peak at around the same latitudes. As our main objective here is to be able to analyze progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints. We edited in full the final paragraph of Section 2.3, as well as parts of the paragraph of Section 3.1 you point out. We trust the new graphs and discussions are clear now. Let us know.

-----------------------------------------------------------------------------------------
Q4. Table 2 summarises the differences of the median values of the DEMT and MHD model. This is OK. However, there is an opportunity here to present a more detailed comparison, including in particular the mean (or median) absolute deviation (MAD) of values between DEMT and MHD. The MAD is a more stringent, voxel-by-voxel test of the comparison, which cannot be seen from the histogram comparisons (e.g. figure 12/13) nor the median values of Table 2.

A4. The populations shown in the histograms are about types of legs associated with different latitudinal regions. The selection of these legs is not the same for AWSoM and DEMT. This is why calculating the MAD a on the relationship of the populations of the histograms reported is not simple. In the future we plan to make a comparative analysis leg-to-leg between AWSoM and DEMT and in that case we will undoubtedly report some statistics associated with the standard deviation such as being the MAD.

-----------------------------------------------------------------------------------------
Q5. You discuss the less reliable results from AIA in coronal holes. The very recent paper by Saqri et al (Solar Physics 295, 2020) is relevant here, and should be referenced.

A5. Thanks for the refernce, certainly relevant and now mentioned in the paper (see below). As mentioned in the discussion section of v1: "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets. We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." We have successfully implemented the improved version of the code, as a result of which this problem has been solved. The issue was related to the algorithm that solves the optimization problem posed in each voxel to find the LDEM. When based on AIA data, the previous algorithm tended to converge to a non-optimal (local minimum of the objective function) in specific voxels located in the CHs. We addressed the problem by exploring multiple starting points when solving the optimization problem in cases where the initial solution was not good enough. In this draft, this improved algorithm affects results concerning type III legs for CR2208. As a result, the following Figures have been updated: 2, 3, 4, 5, 10, 13 and 14. You will notice all these Figures are just like the original ones, except the problem in the CHs of CR-2208 has been solved. Text throughout the manuscript was edited accordingly, in the following locations of v2 of the draft:
 - Second paragraph after Figure 2.
 - Paragraph following Figure 4.
 - Numerical values concerning legs of type-III for CR-2208 in Tables 1 and 2.
 - Most of the third paragraph of the Conclusion section in V1 was devoted to this solved issue, so it was eliminated. The remaining text is now the end of the second paragraph of that section (highlighted in red color).

-----------------------------------------------------------------------------------------
Q6. The abstract can be shortened somewhat, reducing the number of introductory sentences and with a little less emphasis on the method and future improvements, and more on the science results. In particular: the results of the energy balance analysis and the estimate of energy flux at the coronal base, which are important.

A6. (TOTALMENTE, HAGAMOS ESTO LUEGO DE EDITAR TODO).

-----------------------------------------------------------------------------------------
Q7. Page 5, paragraph beginning line 34. You briefly describe fitting the DEM to a Gaussian. I know this approach is covered in detail in Nuevo 2015, but I would like a little more detail here. You should mention that, in general, DEMs do not necessarily have a clean Gaussian profile and that more complicated inversions are needed (reference https://ui.adsabs.harvard.edu/abs/2012A%26A...539A.146H/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..135M/abstract , https://ui.adsabs.harvard.edu/abs/2019SoPh..294..136P/abstract ). Then explain briefly why DEMT leads to cleaner, non-multithermal profiles (due to the 3D spatial reconstruction of the line of sight). I assume that this is why you can use a straightforward Gaussian fit? Also efficiency?

A7. Thanks for this comment and the references. As the LDEM describes the temperature distribution of the plasma in a specific voxel it does not deal with different large scale structures, as it usually it may be the case for the DEM describing the plasma alog a full line-of.sight (LOS). In that sense one can expect as you say, cleaner, profiles than those observed by DEM studies. Still, if one adds tbhe 335 A channel, which adds two sensitivity poits at ~ 1.0 MK and ~ 2.5 MK, one finds that a a bi-Gaussian LDEM model best predics all the tomographic emissivities. That is the main conclusion of Nuevo et. al. (2015). The interpretation in that case is that the unresolved independent strands threading the voxel can have two different characteristic temperatures. Nuevo et al. (2015). So in this sense, the plasma within the voxel can be multi-thermal. As for efficiency, the parametric technique is comparably efficient independently of the chosen model. We did read the  We expanded this discussion in the text.

-----------------------------------------------------------------------------------------
Q8. The introduction does not have many references to works beyond DEMT and AWSoM. The 2nd paragraph of the introduction offers a chance to remedy this, where you discuss the quiet-Sun corona. I know there are very few works that address the quiet corona in the context of DEM analysis, but you can reference https://www.aanda.org/articles/aa/full_html/2014/04/aa23054-13/aa23054-13.html. You can also mention https://iopscience.iop.org/article/10.1088/0004-637X/795/2/111 here (although you do reference this paper in more detail in the discussion). Another relevant paper which can be referenced, with DEM analysis of a large amount of quiet coronal data over long time periods, is https://advances.sciencemag.org/content/3/7/e1602056 .

A8.
ALBERT VA A ESCRIBIR UN POCO DE TEXTO.

LO QUE SIGUE DEBE SER TODO HECHO POR DIEGO, CONSULTANDO PRINCIPALMENTE A ALBERT. TODO CAMBIO DEBERÁ ESTAR DESTACADO CON \EDIT{} EN ROJO.

-----------------------------------------------------------------------------------------
Q9. Some sections can benefit from weeding out of repetitions. You tend to repeat statements regarding the method a lot. For example:
- Paragraph starting page 13, line 41. This has already been said in the method.
- Sentence Page 14, line 25 'For each leg…
- statement in parenthesis at page 15, line 24.
- Section 4, first two paragraphs.
- Page 26, line 26:
 'In the streamer belt region we combined the DEMT results and the AWSom magnetic model to infer the energy input phi at the coronal base required to maintain stable coronal loops. We found characteristic values in the range…'
Shorten to: 'The energy input phi at the coronal base, required to maintain stable coronal loops, is in the range…'
- Page 26, lines 38-43, between 'Results of the AWSoM….summarized as follows.' can be omitted.

A9. Thanks for pointing this out. We have improved the text in the following parts:

-----------------------------------------------------------------------------------------
Q10. Minor grammatical improvements, typos, and removal of redundant statements

A10. Thanks very much for this detailed corrections. We have addressed them all.

Page number, line number: 
3,36: quantitive analysis
3, 44: based on data
4, 25: absent => is this the right choice of word? I would think that the effect of fast dynamics is reduced, rather than being completely absent?
Equation 1 (and subsequent). You use LDEM and TRF. Is it more correct to use Greek symbols rather than acronyms in the equations? However, if you have used these acronyms in equations in previous studies, please leave as is.
6, 9: average absolute relative difference
6, 35: energy partitioning is improved
6, 46: broadened
6, 50 and 51: explain the subscripts for N and T
7, 39: waves is set to L
7, 41: radially stretched => is there a better description? 
7, 41: The spherical grid… has an adaptive grid that has fine resolution near the Sun, and increases…
7, 46: million cells on 6 x 
7, 49: The AWSoM simulation of the solar corona for…to the DEMT in the results section.
8, 23: products are traced
8, 33: For DEMT the data points used are 
8, 48: hereafter, with del_r=e_r.del being the radial derivative operator, and e_r is the 
9, 2: to directly compare the observed
9, 11: , and later by Aschwanden
9, 17: and the heliocentric height r. We then
9, 19: the goodness of fit  we perform
9, 21: uncertainty of the DEMT, selecting legs
9, 24: linear fit to temperature is weak, are excluded
9, 28: according to del_r
9, 31: quality of the fit considers
9, 33: In summary, a selected leg must meet three conditions:
9, 40: temperature and height points must meet
9, 48: four different types:
10, 12: type 0 to II allows a study of the streamer belt in three distinct layers at increasing height.
10, 25: model, as described
10, 35: transverse => cross-sectional?
11, 44: Figures 1 and 2 show …. (omit 'As an example', not needed)
12, 35: Rotation CR-2082 has two small… (and same in following sentence)
13: 34: by Equation 4 show that the agreement… (omit 'in most of the coronal volume of the DEMT grid', not needed)
13: 36: A similar result was
15, 19: to this point in the Conclusions.
15, 28: Caption to table 1. Informed => given? Also explain that the CR-2208 values are given in parenthesis.
15, 42: Table 1 summarises the results of the…
16, 51: , the temperature based on AIA data
17, 45: Considering this error, Figure 5
18, 8: legs, each loop was
18, 20: characterised    by temperatures that are are progressively larger, and farther from T_c, for both rotations.
18, 33: smallest sized loops of type 0, and it is likely due to emission out of the instrumental sensitivity range.
19, 17: axisymmetric, similar to the tomographic results. (In fact, you should avoid using 'tomographic model' since it is not a model, this happens a few times in the text).
19, 45: a visual comparison reveals similar
19, 50: Such a comparison…, with the top
20, 30: are worth highlighting.
20, 43: boundary. Lastly, the DEMT… ('note that' is usually not needed, you use quite a lot in text)
20, 47: For comparison, B_r in the CHs increases from
22, 42: tomografic => tomographic
22, 48: This figure can be compared
22, 49: …DEMT results. The AWSoM maps are more densely populated
22, 50: having spatially smoother distributions of electron density and temperature than those of DEMT.
23, 38: variation relative to the DEMT. (Then omit 'The following major results can be drawn', not needed).
25, 47: Omit 'Concerning the DEMT reconstructions, Figure 3 shows that, for both rotations, …'  Start paragraph with 'Magnetic field lines of type…'
25, 50: Omit 'Figure 5 and Table 1 show in 3D quantitive detail how…', and start sentence with 'These progressively outer'
26, 12: such comparison provided a consistency check. (And omit 'for the changes implemented in the DEMT technique.')
26, 20: less reliable for CHs.
26, 24: algorithm to deal
27, 12: This is likely the cause of a more accurate match to the…
27, 14: Omit first sentence of paragraph, not needed.
27, 30: in the range of
27, 33: This will be investigated in

### 2020-03-10 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

\def\edit#1{\textcolor{Red}{#1}}
\def\del#1{\textcolor{Blue}{#1}}

@@

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type \edit{type 0 to II allows a study of the streamer belt in three distinct layers at increasing height.}}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic} and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below in this section.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
\caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). {Mid panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red and cyan} color, respectively.}\edit{Bottom panels: histograms of the latitudinal distribution at $r=1.105\,\mrsun$ of the selected legs.}}
\label{rpoint_demt}
\end{center}
\end{figure}

For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. \del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the \edit{mid} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red and cyan} color, respectively. \edit{The bottom panels of same figure shows histograms of the latitudinal distribution of the legs using same color code.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III. On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.

{Type 0 (small down) legs mainly populate the equatorial latitudes. This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}. Here, we verify the existence of this type of structure for the two rotations. The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. Type I (small up) mainly populate the mid-latitudes, while type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt. Finally, type III (open) legs populate the CHs.}

@@

Figure \ref{gradt_demt} shows frequency histograms of $\dr\Tm$ for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$ for legs of type 0, I, II and III, respectively.}
\del{
{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs. We will return to this point in the {Conclusions}.}
}

@@

\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II \edit{were selected to be associated} with increasingly outer {layers} of the equatorial streamer belt. \del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.}

{{For both rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer. In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy. As a result, DEMT results based on AIA data {are less reliable \edit{for} CHs}. This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}. The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets. We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article.}

>>>>

\def\edit#1{\textcolor{Red}{#1}}
\def\del#1{\textcolor{Blue}{#1}}
\def\comment#1{\textcolor{Blue}{#1}}

@@

\edit{Legs of type down turn out to have a significant population only for closed-small field lines. Hence, we separate them into two complementary classes: legs of type 0 (down) and legs of type I (up). In the case of closed-large field lines, legs of type down are $\lesssim 15\%$ of the population. In the case of open field lines, legs of type down are $\lesssim 10\%$ of the population. Hence, the requirement of being up for legs of type II and III is included to select the vastly dominating population in each case. On the other hand, the inclusion of latitude limits for the footpoints in the classification of legs from type 0 through III is purposely set to study the streamer belt in three distinct, progressively outer layers, as well as to separate the field lines of the high latitude CHs (legs of type III). In Section \ref{resu}, the results of both the DEMT and AWSoM models in the four classes of legs are statistically analysed.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT {products $\sqravgN$} (left panels) and $\Tm$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries. \comment{Por consistencia, creo que en los títulos de los CarrMaps de las Figuras 1 y 2 deberías usar la notación $\sqravgN$ y $\Tm$. Si esto lo hacés en LETITBE con el IDL 8.4, podrás usar los comandos de LaTeX dentro de las strings ``title", con lo cual no solo será simple sino que $\sqravgN$ no va a ocupar mucho más espacio y las chances son que salga todo lindo sin cambiar el tamaño de letra ni nada.}}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that \edit{the agreement between the tomographic and synthetic FBEs meets $R \lesssim 0.01$ in more than 90\% of the voxels where tomographic reconstruction is possible (i.e. where FBEs are non zero), and meets $R \lesssim 0.10$ in the rest. This implies that the LDEM found in each voxel accurately predicts the reconstructed FBEs.} \comment{Diego, evaluá que el valor que incluí es correcto. Simplemente fijate en que fracción de los voxels SIN ZDAs $R<0.01$ para CR-2208, yo estimo $90\%$. pra 2082 no hace falta. Comentame antes de enviar.}

. The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below in this section.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
\caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). \edit{Middle panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red, and cyan} color, respectively.} \edit{Bottom panels: frequency histograms of the latitude of the four types of legs of the middle panel.}}
\label{rpoint_demt}
\end{center}
\end{figure}

For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. \del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the \edit{middle} panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, \edit{orange, red, and cyan} color, respectively. \edit{The bottom panels show histograms of the latitude distribution of the legs of the middle panel, using the same color code.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III. On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.

\edit{For both rotations, the population of type 0 (small-closed-down) legs population peaks in the core of the streamer belt, around the equator in the case of CR-2082, and towards the southern hemisphere in the case of CR-2208.} This kind of structure was originally found by \citet{huang_2012}, and their existence was shown to be anti-correlated with the solar activity level around the solar minimum between {SCs 23 and 24} by \citet{nuevo_2013}. Later on, \citet{lloveras_2017} showed {that} equatorial down loops in streamers were also to be found in the deep minimum between SCs {23 and 24}. Here, we verify the existence of this type of structure for the two rotations. The relatively smaller population of down legs seen in CR-2208, as compared to CR-2082, is consistent with the aforementioned results by \citet{nuevo_2013}. \edit{Type I (small-closed-up) legs are present at all latitudes in the streamer belt. Their population peaks in the mid-latitudes of both hemispheres for CR-2082, and in the mid-latitudes of the northern hemisphere for CR-2208. Type II (large up) legs are mostly very large trans-equatorial field lines forming the envelope of the streamer belt (the requirement of footpoints located beyond mid-latitudes was included precisely to select this kind of loop). Finally, type III (open) legs populate the high latitude CHs.}

@@

Figure \ref{gradt_demt} shows frequency histograms of $\dr\Tm$ for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$, for legs of type 0, I, II and III, respectively.}

@@

\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II \edit{were selected to be associated} with increasingly outer {layers} of the equatorial streamer belt. \del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.} \edit{For both rotations, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer.}
